Tutorial_2a

### 2024-12-02 Tutorial_2a.Rmd
add 2a html
update 2a rmd and html

```{r ppc-manual, eval=T}
# prior predictive check for 1 time bin
# see http://bruno.nicenboim.me/bayescogsci/

@@

```{r inspect-M0i}
model_M0i <- readRDS("Tutorial_2_Bayesian/models/model_M0i.rds")
summary(model_M0i)
plot(model_M0i)
```

>>>>

```{r ppc-manual, eval=F}
# prior predictive check for 1 time bin
# see http://bruno.nicenboim.me/bayescogsci/

@@

```{r inspect-M0i}
model_M0i <- readRDS("Tutorial_2_Bayesian/models/model_M0i.rds")
summary(model_M0i)
#plot(model_M0i)
```
